\documentclass{article}

\title{\textbf{
Exercises from \\
\textit{Everything} \\
by All Authors
}}

\date{}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}

\begin{document}
\maketitle

\paragraph{Herstein.exercise.2.1.18} If $G$ is a finite group of even order, prove that $G$ contains an element of order $2$.

\paragraph{Herstein.exercise.2.1.26} If $G$ is a finite group, then every element of $G$ has finite order.

\paragraph{Herstein.exercise.2.2.3} Let $G$ be a group. Suppose that for some $n$, the following three statements hold:
\begin{enumerate}
\item $a^n b^n = b^n a^n$ for all $a, b \in G$.
\item $a^{n+1} b^{n+1} = b^{n+1} a^{n+1}$ for all $a, b \in G$.
\item $a^{n+2} b^{n+2} = b^{n+2} a^{n+2}$ for all $a, b \in G$.
\end{enumerate}
Prove that $G$ is abelian.

\paragraph{Herstein.exercise.2.2.6c} Let $G$ be a group and let $n$ be a positive integer. Suppose that $a^n=b^n$ implies $ab=ba$ for all $a, b \in G$. Prove that $(abab^{-1}a^{-1})^{n(n-1)}=1$ for all $a, b \in G$.

\paragraph{Herstein.exercise.2.3.16} Prove that a group $G$ is cyclic if and only if every subgroup of $G$ is either trivial or the whole group.

\paragraph{Herstein.exercise.2.5.23} Let $G$ be a group in which every subgroup is normal. Prove that for any $a, b \in G$, there exists $j \in \mathbb{Z}$ such that $b*a = a^j*b$.

\paragraph{Herstein.exercise.2.5.31} If $G$ is a finite group of order $p^nm$ where $p$ is prime and $p$ does not divide $m$, then the subgroup of order $p^n$ is characteristic.

\paragraph{Herstein.exercise.2.5.43} Prove that a group of order $9$ is abelian.

\paragraph{Herstein.exercise.2.5.52} Let $G$ be a finite group and let $\phi$ be an automorphism of $G$. If $|I|>3/4|G|$ and $\phi(x)=x^{-1}$ for all $x\in I$, then $\phi(x)=x^{-1}$ for all $x\in G$ and $G$ is abelian.

\paragraph{Herstein.exercise.2.7.7} If $N$ is a normal subgroup of $G$ and $\phi:G\to G'$ is a homomorphism, then $\phi(N)$ is a normal subgroup of $G'$.
\end{document}