\documentclass{article}

\title{ProofNet NL Statements}
\author{Zhangir Azerbayev}
\date{Summer 2022}

\usepackage{amsmath}
\usepackage{amssymb}

\setlength{\parindent}{0pt}

\begin{document}
\maketitle
\section{df}
\subsection*{chapter 1}
\subsubsection*{section 1}
15: Prove that $(a_1a_2\dots a_n)^{-1} = a_n^{-1}a_{n-1}^{-1}\dots a_1^{-1}$ for all $a_1, a_2, \dots, a_n\in G$. 

16: Let $x$ be an element of $G$. Prove that $x^2=1$ if and only if $x|x|$ is either $1$ or $2$. 

17: Let $x$ be an element of $G$. Prove that if $|x|=n$ for some positive integer $n$ then $x^{-1}=x^{n-1}$. 

18: Let $x$ and $y$ be elements of $G$. Prove that $xy=yx$ if and only if $y^{-1}xy=x$ if and only if $x^{-1}y^{-1}xy=1$.

20: For $x$ an element in $G$ show that $x$ and $x^{-1}$ have the same order.

22a: If $x$ and $g$ are elements of the group $G$, prove that $|x|=\left|g^{-1} x g\right|$. 

22b: Deduce that $|a b|=|b a|$ for all $a, b \in G$.

25: Prove that if $x^{2}=1$ for all $x \in G$ then $G$ is abelian.

29: Prove that $A \times B$ is an abelian group if and only if both $A$ and $B$ are abelian.

34: If $x$ is an element of infinite order in $G$, prove that the elements $x^{n}, n \in \mathbb{Z}$ are all distinct.

\subsubsection*{section 3}
8: Prove that if $\Omega=\{1,2,3, \ldots\}$ then $S_{\Omega}$ is an infinite group

\subsubsection*{section 6}
4: Prove that the multiplicative groups $\mathbb{R}-\{0\}$ and $\mathbb{C}-\{0\}$ are not isomorphic.

11: Let $A$ and $B$ be groups. Prove that $A \times B \cong B \times A$.

12: Let $A$ and $B$ be groups. Prove that $A \times B \cong B \times A$.

17: Let $G$ be any group. Prove that the map from $G$ to itself defined by $g \mapsto g^{-1}$ is a homomorphism if and only if $G$ is abelian.

23: Let $G$ be a finite group which possesses an automorphism $\sigma$ such that $\sigma(g)=g$ if and only if $g=1$. If $\sigma^{2}$ is the identity map from $G$ to $G$, prove that $G$ is abelian 

\subsubsection*{section 7}
5: 

6: 

\end{document}
