\documentclass{article}

\title{\textbf{
Exercises from \\
\textit{Cambridge Tripos}
}}

\date{}

\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}
\maketitle

\paragraph{Exercise 2022.IA.1-II-9D-a} Let $a_{n}$ be a sequence of real numbers. Show that if $a_{n}$ converges, the sequence $\frac{1}{n} \sum_{k=1}^{n} a_{k}$ also converges and $\lim _{n \rightarrow \infty} \frac{1}{n} \sum_{k=1}^{n} a_{k}=\lim _{n \rightarrow \infty} a_{n}$.

\paragraph{Exercise 2022.IA.1-II-10D-c} Let a function $g:(0, \infty) \rightarrow \mathbb{R}$ be continuous and bounded. Show that for every $T>0$ there exists a sequence $x_{n}$ such that $x_{n} \rightarrow \infty$ and $\lim _{n \rightarrow \infty}\left(g\left(x_{n}+T\right)-g\left(x_{n}\right)\right)=0 .$

\paragraph{Exercise 2022.IA.4-I-1E-a} By considering numbers of the form $3 p_{1} \ldots p_{k}-1$, show that there are infinitely many primes of the form $3 n+2$ with $n \in \mathbb{N}$.

\paragraph{Exercise 2022.IA.4-I-2D-a} Prove that $\sqrt[3]{2}+\sqrt[3]{3}$ is irrational.

\paragraph{Exercise 2022.IB.3-II-13G-a-i} Let $U \subset \mathbb{C}$ be a (non-empty) connected open set and let $f_n$ be a sequence of holomorphic functions defined on $U$. Suppose that $f_n$ converges uniformly to a function $f$ on every compact subset of $U$. Show that $f$ is holomorphic in $U$.

\paragraph{Exercise 2022.IB.3-II-11G-b} Let $f: \mathbb{R}^{2} \rightarrow \mathbb{R}^{2}$ be the map given by $f(x, y)=\left(\frac{\cos x+\cos y-1}{2}, \cos x-\cos y\right)$. Prove that $f$ has a fixed point.

\paragraph{Exercise 2022.IB.1-I-3G-i} Show that $f(z)=\frac{z}{\sin z}$ has a removable singularity at $z=0$.

\paragraph{Exercise 2022.IB.3-I-1E-ii} Let $R$ be a subring of a ring $S$, and let $J$ be an ideal in $S$. Show that $R+J$ is a subring of $S$ and that $\frac{R}{R \cap J} \cong \frac{R+J}{J}$.

\paragraph{Exercise 2022.IIB.1-II-8F-a-i} Let $V$ be a finite dimensional complex inner product space, and let $\alpha$ be an endomorphism of $V$. Define its adjoint $\alpha^*$. Assume that $\alpha$ is normal, i.e. $\alpha$ commutes with its adjoint: $\alpha \alpha^*=\alpha^* \alpha$. Show that $\alpha$ and $\alpha^*$ have a common eigenvector $\mathbf{v}$.

\paragraph{Exercise 2021.IIB.3-II-11F-ii} Let $X$ be an open subset of Euclidean space $\mathbb{R}^n$. Show that $X$ is connected if and only if $X$ is path-connected.

\paragraph{Exercise 2021.IIB.2-I-1G} Let $M$ be a module over a Principal Ideal Domain $R$ and let $N$ be a submodule of $M$. Show that $M$ is finitely generated if and only if $N$ and $M / N$ are finitely generated.

\paragraph{Exercise 2021.IIB.3-I-1G-i} Let $G$ be a finite group, and let $H$ be a proper subgroup of $G$ of index $n$. Show that there is a normal subgroup $K$ of $G$ such that $|G / K|$ divides $n$ ! and $|G / K| \geqslant n$

\paragraph{Exercise 2021.IIB.1-II-9G-v} Let $R$ be the ring of continuous functions $\mathbb{R}\to\mathbb{R}$. Show that $R$ is not Noetherian.

\paragraph{Exercise 2018.IA.1-I-3E-b} Let $f: \mathbb{R} \rightarrow(0, \infty)$ be a decreasing function. Let $x_{1}=1$ and $x_{n+1}=x_{n}+f\left(x_{n}\right)$. Prove that $x_{n} \rightarrow \infty$ as $n \rightarrow \infty$.

\end{document}
