\documentclass{article}

\title{\textbf{
Exercises from \\
\textit{Real Mathematical Analysis} \\
by Charles Pugh
}}

\date{}

\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}
\maketitle


\paragraph{Exercise 2.12a} Let $(p_n)$ be a sequence and $f:\mathbb{N}\to\mathbb{N}$. The sequence $(q_k)_{k\in\mathbb{N}}$ with $q_k=p_{f(k)}$ is called a rearrangement of $(p_n)$. Show that if $f$ is an injection, the limit of a sequence is unaffected by rearrangement.

\paragraph{Exercise 2.12b} Let $(p_n)$ be a sequence and $f:\mathbb{N}\to\mathbb{N}$. The sequence $(q_k)_{k\in\mathbb{N}}$ with $q_k=p_{f(k)}$ is called a rearrangement of $(p_n)$. Show that if $f$ is a surjection, the limit of a sequence is unaffected by rearrangement.

\paragraph{Exercise 2.26} Prove that a set $U \subset M$ is open if and only if none of its points are limits of its complement.

\paragraph{Exercise 2.29} Let $\mathcal{T}$ be the collection of open subsets of a metric space $\mathrm{M}$, and $\mathcal{K}$ the collection of closed subsets. Show that there is a bijection from $\mathcal{T}$ onto $\mathcal{K}$.

\paragraph{Exercise 2.32a} Show that every subset of $\mathbb{N}$ is clopen.

\paragraph{Exercise 2.41} Let $\|\cdot\|$ be any norm on $\mathbb{R}^{m}$ and let $B=\left\{x \in \mathbb{R}^{m}:\|x\| \leq 1\right\}$. Prove that $B$ is compact.

\paragraph{Exercise 2.46} Assume that $A, B$ are compact, disjoint, nonempty subsets of $M$. Prove that there are $a_0 \in A$ and $b_0 \in B$ such that for all $a \in A$ and $b \in B$ we have $d(a_0, b_0) \leq d(a, b)$.

\paragraph{Exercise 2.48} Prove that there is an embedding of the line as a closed subset of the plane, and there is an embedding of the line as a bounded subset of the plane, but there is no embedding of the line as a closed and bounded subset of the plane.

\paragraph{Exercise 2.56} Prove that the 2-sphere is not homeomorphic to the plane.

\paragraph{Exercise 2.57} Show that if $S$ is connected, it is not true in general that its interior is connected.

\paragraph{Exercise 2.79} Prove that if $M$ is nonempty compact, locally path-connected and connected then it is path-connected.

\paragraph{Exercise 2.85} Suppose that $M$ is compact and that $\mathcal{U}$ is an open covering of $M$ which is redundant in the sense that each $p \in M$ is contained in at least two members of $\mathcal{U}$. Show that $\mathcal{U}$ reduces to a finite subcovering with the same property.

\paragraph{Exercise 2.92} Give a direct proof that the nested decreasing intersection of nonempty covering compact sets is nonempty.

\paragraph{Exercise 2.109} A metric on $M$ is an ultrametric if for all $x, y, z \in M$, $d(x, z) \leq \max \{d(x, y), d(y, z)\} .$ Show that a metric space with an ultrametric is totally disconnected.

\paragraph{Exercise 2.126} Suppose that $E$ is an uncountable subset of $\mathbb{R}$. Prove that there exists a point $p \in \mathbb{R}$ at which $E$ condenses.

\paragraph{Exercise 2.137} Let $P$ be a closed perfect subset of a separable complete metric space $M$. Prove that each point of $P$ is a condensation point of $P$.

\paragraph{Exercise 2.138} Given a Cantor space $M \subset R^2$, given a line segment $[p, q] \subset R^2$ with $p, q \not\in M$, and given an $\epsilon > 0$, prove that there exists a path $A$ in the $\epsilon$-neighborhood of $[p, q]$ that joins $p$ to $q$ and is disjoint from $M$.

\paragraph{Exercise 3.1} Assume that $f \colon \mathbb{R} \rightarrow \mathbb{R}$ satisfies $|f(t)-f(x)| \leq|t-x|^{2}$ for all $t, x$. Prove that $f$ is constant.

\paragraph{Exercise 3.4} Prove that $\sqrt{n+1}-\sqrt{n} \rightarrow 0$ as $n \rightarrow \infty$.

\paragraph{Exercise 3.11a} Let $f \colon (a, b) \rightarrow \mathbb{R}$ be given.  If $f''(x)$ exists, prove that \[\lim_{h \rightarrow 0} \frac{f(x - h) - 2f(x) + f(x + h)}{h^2} = f''(x).\]

\paragraph{Exercise 3.17c-i} Show that the bump function $\beta(x)=e^{2} e(1-x) \cdot e(x+1)$ is smooth.

\paragraph{Exercise 3.17c-ii} Show that the bump function $\beta(x)=e^{2} e(1-x) \cdot e(x+1)$ is identically 0 outside the interval $(-1, 1)$.

\paragraph{Exercise 3.18} Let $L$ be any closed set in $\mathbb{R}$. Prove that there is a smooth function $f \colon \mathbb{R} \rightarrow [0, 1]$ such that $f(x) = 0$ if and only if $x \in L$.

\paragraph{Exercise 3.43a} Let $\psi(x) = x \sin 1/x$ for $0 < x \leq 1$ and $\psi(0) = 0$.  If $f \colon [-1, 1] \rightarrow \mathbb{R}$ is Riemann integrable, prove that $f \circ \psi$ is Riemann integrable.

\paragraph{Exercise 3.53} Given $f, g \in \mathcal{R}$, prove that $\max(f, g)$ and $\min(f, g)$ are Riemann integrable, where $\max(f, g)(x) = \max(f(x), g(x))$ and $\min(f, g)(x) = \min(f(x), g(x))$.

\paragraph{Exercise 3.63a} Prove that $\sum 1/k(\log(k))^p$ converges when $p > 1$.

\paragraph{Exercise 3.63b} Prove that $\sum 1/k(\log(k))^p$ diverges when $p \leq 1$.

\paragraph{Exercise 4.15a} A continuous, strictly increasing function $\mu \colon (0, \infty) \rightarrow (0, \infty)$ is a modulus of continuity if $\mu(s) \rightarrow 0$ as $s \rightarrow 0$. A function $f \colon [a, b] \rightarrow \mathbb{R}$ has modulus of continuity $\mu$ if $|f(s) - f(t)| \leq \mu(|s - t|)$ for all $s, t \in [a, b]$. Prove that a function is uniformly continuous if and only if it has a modulus of continuity.

\paragraph{Exercise 4.15b} A continuous, strictly increasing function $\mu \colon (0, \infty) \rightarrow (0, \infty)$ is a modulus of continuity if $\mu(s) \rightarrow 0$ as $s \rightarrow 0$. A function $f \colon [a, b] \rightarrow \mathbb{R}$ has modulus of continuity $\mu$ if $|f(s) - f(t)| \leq \mu(|s - t|)$ for all $s, t \in [a, b]$. Prove that a family of functions is equicontinuous if and only if its members have a common modulus of continuity.

\paragraph{Exercise 4.19} If $M$ is compact and $A$ is dense in $M$, prove that for each $\delta > 0$ there is a finite subset $\{a_1, \ldots , a_k\} \subset A$ which is $\delta$-dense in $M$ in the sense that each $x \in M$ lies within distance $\delta$ of at least one of the points $a_1,\ldots, a_k$.

\paragraph{Exercise 4.36a} Suppose that the ODE $x' = f(x)$ on $\mathbb{R}$ is bounded, $|f(x)| \leq M$ for all x. Prove that no solution of the ODE escapes to infinity in finite time.

\paragraph{Exercise 4.42} Prove that $\mathbb{R}$ cannot be expressed as the countable union of Cantor sets.

\paragraph{Exercise 5.2} Let $L$ be the vector space of continuous linear transformations from a normed space $V$ to a normed space $W$. Show that the operator norm makes $L$ a normed space.

\paragraph{Exercise 5.20} Assume that $U$ is a connected open subset of $\mathbb{R}^n$ and $f \colon U \rightarrow \mathbb{R}^m$ is differentiable everywhere on $U$. If $(Df)_p = 0$ for all $p \in U$, show that $f$ is constant.

\paragraph{Exercise 5.22} If $Y$ is a metric space and $f \colon [a, b] \times Y \rightarrow \mathbb{R}$ is continuous, show that $F(y) = \int^b_a f(x,y) dx$ is continuous.

\paragraph{Exercise 5.43a} Suppose that $T \colon R^n \rightarrow R^m$ has rank $k$.  Show there exists a $\delta > 0$ such that if $S \colon R^n \rightarrow R^m$ and $||S - T|| < \delta$ then $S$ has rank $\geq k$.

\paragraph{Exercise 6.38} If $f$ and $g$ are integrable prove that their maximum and minimum are integrable.

\paragraph{Exercise 6.39} Suppose that $f$ and $g$ are measurable and their squares are integrable. Prove that $fg$ is measurable, integrable, and $\int fg \leq \sqrt{\int f^2} \sqrt{\int g^2}$.

\paragraph{Exercise 6.43} Prove that $g(y) = \int_0^\infty e^{-x} \sin(x + y) dx$ is differentiable and find $g'(y)$.

\paragraph{Exercise 6.49a} Prove that $f \colon \mathbb{R} \rightarrow \mathbb{R}$ is Lebesgue measurable if and only if the preimage of every Borel set is a Lebesgue measurable.


\end{document}
