\documentclass{article}

\title{\textbf{
Exercises from \\
\textit{Real Mathematical Analysis} \\
by Charles Pugh
}}

\date{}

\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}
\maketitle


\paragraph{Exercise 2.12a} Let $(p_n)$ be a sequence and $f:\mathbb{N}\to\mathbb{N}$ a bijection. The sequence $(q_k)_{k\in\mathbb{N}}$ with $q_k=p_{f(k)}$ is called a rearrangement of $(p_n)$. Show that if $f$ is an injection, the limit of a sequence is unaffected by rearrangement.

\paragraph{Exercise 2.12b} Let $(p_n)$ be a sequence and $f:\mathbb{N}\to\mathbb{N}$ a bijection. The sequence $(q_k)_{k\in\mathbb{N}}$ with $q_k=p_{f(k)}$ is called a rearrangement of $(p_n)$. Show that if $f$ is a surjection, the limit of a sequence is unaffected by rearrangement.

\paragraph{Exercise 2.26} Prove that a set $U \subset M$ is open if and only if none of its points are limits of its complement.

\paragraph{Exercise 2.29} Let $\mathcal{T}$ be the collection of open subsets of a metric space $\mathrm{M}$, and $\mathcal{K}$ the collection of closed subsets. Show that there is a bijection from $\mathcal{T}$ onto $\mathcal{K}$.

\paragraph{Exercise 2.32a} Show that every subset of $\mathbb{N}$ is clopen.

\paragraph{Exercise 2.41} Let $\|\cdot\|$ be any norm on $\mathbb{R}^{m}$ and let $B=\left\{x \in \mathbb{R}^{m}:\|x\| \leq 1\right\}$. Prove that $B$ is compact.

\paragraph{Exercise 2.46} Assume that $A, B$ are compact, disjoint, nonempty subsets of $M$. Prove that there are $a_0 \in A$ and $b_0 \in B$ such that for all $a \in A$ and $b \in B$ we have $d(a_0, b_0) \leq d(a, b)$.

\paragraph{Exercise 2.48} Prove that there is an embedding of the line as a closed subset of the plane, and there is an embedding of the line as a bounded subset of the plane, but there is no embedding of the line as a closed and bounded subset of the plane.

\paragraph{Exercise 2.56} Prove that the 2-sphere is not homeomorphic to the plane.

\paragraph{Exercise 2.57} Show that if $S$ is connected, it is not true in general that its interior is connected.

\paragraph{Exercise 2.79} Prove that if $M$ is nonempty compact, locally path-connected and connected then it is path-connected.

\paragraph{Exercise 2.85} Suppose that $M$ is compact and that $\mathcal{U}$ is an open covering of $M$ which is "redundant" in the sense that each $p \in M$ is contained in at least two members of $\mathcal{U}$. Show that $\mathcal{U}$ reduces to a finite subcovering with the same property.

\paragraph{Exercise 2.92} Give a direct proof that the nested decreasing intersection of nonempty covering compact sets is nonempty.

\paragraph{Exercise 2.109} A metric on $M$ is an ultrametric if for all $x, y, z \in M$, $d(x, z) \leq \max \{d(x, y), d(y, z)\} .$ Show that a metric space with an ultrametric is totally disconnected.

\paragraph{Exercise 2.126} Suppose that $E$ is an uncountable subset of $\mathbb{R}$. Prove that there exists a point $p \in \mathbb{R}$ at which $E$ condenses.

\paragraph{Exercise 2.137} Let $P$ be a closed perfect subset of a separable complete metric space $M$. Prove that each point of $P$ is a condensation point of $P$.

\paragraph{Exercise 2.138} Given a Cantor space $M \subset R^2$, given a line segment $[p, q] \subset R^2$ with $p, q \not\in M$, and given an $\epsilon > 0$, prove that there exists a path $A$ in the $\epsilon$-neighborhood of $[p, q]$ that joins $p$ to $q$ and is disjoint from $M$.

\paragraph{Exercise 3.1} Assume that $f \colon \mathbb{R} \rightarrow \mathbb{R}$ satisfies $|f(t)-f(x)| \leq|t-x|^{2}$ for all $t, x$. Prove that $f$ is constant.

\paragraph{Exercise 3.4} Prove that $\sqrt{n+1}-\sqrt{n} \rightarrow 0$ as $n \rightarrow \infty$.

\paragraph{Exercise 3.17c-i} Show that the bump function $\beta(x)=e^{2} e(1-x) \cdot e(x+1)$ is smooth.

\paragraph{Exercise 3.17c-ii} Show that the bump function $\beta(x)=e^{2} e(1-x) \cdot e(x+1)$ is identically 0 outside the interval $(-1, 1)$.

\end{document}
